%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{thebibliography}{00}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\bibitem{bib:ILDcoll} ILD collaboration web page: \\
{\it https://confluence.desy.de/display/ILD/The+ILD+Organisation}.

\bibitem{bib:root} ROOT web page: {\it https://root.cern.ch/}.

\bibitem{bib:BelleHelixParam} Y.~Ohnishi, {\it Track  parameterization}, KEK, National laboratory of high energy physics, Tsukuba, Japan, 1997. \\
%{\tt http://citeseerx.ist.psu.edu/viewdoc/download?doi=10.1.1.23.2827\&rep=rep1\&type=pdf}.

\bibitem{bib:ILD_FPCCD_TrackFinder} T.~Mori {\it et al.}, {\it Study of Tracking and Flavour Tagging with FPCCD Vertex Detector}, 
{\it Proceedings of the International Workshop on Future Linear Colliders (LCWS13)}, 11-15 November 2013, Tokyo, Japan. 
arXiv:1403.5659 [physics.ins-det].

\bibitem{bib:SiDcoll} SiD collaboration web page: {\it http://pages.uoregon.edu/silicondetector/}.

\bibitem{bib:ALICE_ITS_Upgrade} B.~Abelev {\it et al.} [ALICE collaboration], {\it Technical Design Resport for the Upgrade of the ALICE Inner Tracker System}. 
See also: {\tt http://aliceinfo.cern.ch/ITSUpgrade/}.

\bibitem{bib:ILDTracking} F.~Gaede {\it et al.} [ILD collaboration], {\it Track reconstruction at the ILC: the ILD tracking software}, 
{\it Journal of Physics: Conference Series} {\bf 513} (2014) 022011. doi:10.1088/1742-6596/513/2/022011.

\bibitem{bib:ATLASItk} S.~Terzo [ATLAS collaboration], {\it The Phase-II ATLAS ITk pixel upgrade}, {\it Journal of Instrumentation}, Volume 12, July 2017.

\bibitem{bib:CMSTrackerUpgrade} S.~Mersi [CMS collaboration], {\it Phase-2 Upgrade of the CMS Tracker}, {\it Nucl. Part. Phys. Proc.} 273-275 (2016) 1034-1041 (2016-06-02).
DOI: 10.1016/j.nuclphysbps.2015.09.162.

\bibitem{bib:BelleIIcoll} Belle-II web page: {\tt https://www.belle2.org/}.

\bibitem{bib:LHCb_tracker_upgrade} A.~Alves {\it et al} [LHCb collaboration], {\it LHCb Tracker Upgrade Technical Design Report}, CERN-LHCC-2014-001, LHCB-TDR-015.

\bibitem{bib:FOOT_tracker} V.~Patera {\it et al}, {\it The Foot (Fragmentation Of Target) Experiment}, {\it Proceedings of the 26th International Nuclear Physics Conference} 
(INPC2016). 11-16 September, 2016. Adelaide, Australia. FOOT web page: {\tt https://web.infn.it/f00t/index.php/it/}.

\bibitem{bib:MS_angle} K.A. Olive {\it et al.} ({\it Particle Data Group}), Chin. Phys. C, {\bf 38}, 090001 (2014). 

\bibitem{bib:ALICE_fastsim} A. Mastroserio {\it et al.}, {\it Simulation tools for the ALICE ITS Upgrade}, 
{\small{\it http://aliceinfo.cern.ch/ITSUpgrade/sites/aliceinfo.cern.ch.ITSUpgrade/files/documents/Upgrade\_IN.pdf}}.

\end{thebibliography}

